---
title: "Title Goes Here"
author: "Author Name"
date: "`r format(Sys.Date(),'%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE,
                      message = F,
                      warning = F,
                      fig.showtext = TRUE,
                      dpi = 72)
```

## Background

A __Brief__ summary of the project's *background*. Provide the context to the business question at hand, before moving on to a more in-depth __analysis plan__ in subsequent sections.

## The Data

```{r loadData}

```


## Analysis

### Business Question 1

What is the business question this analysis will address?

#### Actionable Approach

Outline and undertake the steps to answer the above question, such as model types, visualizations and/or comparisons.[^robinson]

```{r analysis}

```


## Future Work

## Session Info

Analysis and Report generated on `r sessionInfo()[["running"]]` using `r sessionInfo()[["R.version"]]$version.string`.

```{r dependencies, results='asis'}
# Lists attached packages
function(...) {
  packages <- sessioninfo::package_info(...)

  p <- sprintf("%s (%s)",
               packages$package[packages$attached == T],
               packages$loadedversion[packages$attached == T])

  for (x in p) {
    cat("- ", x, "\n")
  }

}
```

<!-- Insert Footnotes Below -->
[^robinson]: Emily Robinson and Jacqueline Nolis. [Build a Career in Data Science](https://www.manning.com/books/build-a-career-in-data-science#toc). April 2020.
